NumPy---Array Programming in Python

### 2020-01-24 body.tex
Rewrite first paragraph of interoperability

Given the proliferation of array implementations, a widespread adoption of the
NumPy API remains valuable: it lowers the barrier to entry for newcomers, and
provides the wider community with a stable array programming interface.

What can NumPy do to support the use of its API without blocking innovation?
We believe that having NumPy as a central point of coordination between array
objects can improve interoperability while supporting growth of a larger
surrounding ecosystem of specialized solutions and new tools.  Primarily, there
exist two types of Python array objects: (1) arrays that mimic NumPy arrays but are
fundamentally different and (2) subclasses of NumPy arrays.

>>>>

NumPy supports array operations between external array objects by
acting as a central coordination mechanism with a well-specified API.
With the proliferation of array implementations discussed above, a
widespread adoption of the NumPy API is valuable: it lowers the
barrier to entry for newcomers and provides the wider community with a
stable array programming interface. This, in turn, prevents disruptive
schisms like the divergence of Numeric and NumArray, by facilitating
the development of specialized solutions and new tools that operate in
concert.

Primarily, there
exist two types of Python array objects: (1) arrays that mimic NumPy arrays but are
fundamentally different and (2) subclasses of NumPy arrays.
